### 2016-11-23 local-capability-machine.tex
Changed malloc specification and added a bit of a proof

\begin{specification}[Malloc v.2]
  $c_\malloc$ satisfies the specification for malloc iff
\[  
  \left\{
  \begin{aligned}
    &\forall \Phi \in \ExecConfs \ldotp \forall m_{\var{footprint}} \in \Heaps\ldotp \hsframe \in \HeapSegments \ldotp \\
    &\quad \forall n, \size \in \nats \ldotp \forall b,e,a \in \Addrs\ldotp\forall p \in \Perms \ldotp \forall W \in \Worlds \ldotp\\
    &\qquad \exists i, \iota_{\malloc,0} \ldotp \\
    &\qquad \quad \forall W \futurewk [i \mapsto \iota_{\malloc,0}] \land \\
    &\qquad \quad \memheap = m_{\var{footprint}} \uplus \hsframe \land\\
    &\qquad \quad \heapSat[m_{\var{footprint}}]{n}{W} \land \\
    &\qquad \quad \memreg(r_1) = \size \land \\
    &\qquad \quad \size \geq 0 \land \\
    &\qquad \quad \memreg(r_0) = (p,b,e,a) \land \\
    &\qquad \quad \memreg(\pcreg) = c_\malloc \\ %and this needs to change with ABI.
    &\qquad \quad \Rightarrow \\
    &\qquad \qquad\exists \Phi' \in \ExecConfs \ldotp \exists m_{\var{footprint}}' \in \Heaps\ldotp \exists \ms_{\var{alloc}} \in \HeapSegments\ldotp\\
    &\qquad \qquad \quad \exists j,k \in \nats \ldotp \exists b',e'\in \Addrs \ldotp \exists W' \in \Worlds \ldotp \\
    &\qquad \qquad \qquad \Phi \step[j]\Phi' \land \\
    &\qquad \qquad \qquad \memheap[\Phi']=m_{\var{footprint}}' \uplus \hs_{\var{alloc}} \uplus \hsframe \land\\
    &\qquad \qquad \qquad W'(i) = \iota_{\malloc}' \land W' \futurewk W \land \\
    &\qquad \qquad \qquad \heapSat[m_{\var{footprint}}']{n-j}{W'} \land \\
    &\qquad \qquad \qquad \dom(\hs_{\var{alloc}}) = [b',e'] \land \forall a \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0  \land \\
    &\qquad \qquad \qquad \memreg[\Phi'] = \memreg[\Phi]\update{\pcreg}{\updatePcPerm{(p,b,e,a)}}\update{r_1}{((\rwx,\glob),b',e',b')} \land \\
    &\qquad \qquad \qquad \size = e'-b' \land\\
  \end{aligned}\right.
\]
where $\iota_{\malloc,0}$ is the region that initially governs malloc 
\end{specification}
In the specfication above $\iota_\malloc'$ is a future region of the initial region that governs malloc.

@@

\begin{lemma}[Correctness lemma for \texttt{f1}] \forcenewline
\label{lem:correctness-f1}
  For all $n \in \nats$
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+2) \\
    c_{f1} & \defeq ((\rwx,\glob),\mathtt{f1}-2,\mathtt{1f},\mathtt{f1}) \\
    c_\malloc & \defeq ((\entry,\glob),\start_\malloc,\addrend_\malloc,\start_\malloc+2) \\
    m & \defeq \hs_{f1} \uplus 
               \hs_\flag \uplus                
               \ms_{\var{link}} \uplus 
               \hs_\adv \uplus 
               m_{\malloc} \uplus 
               \hs_{\var{frame}} 
  \end{align*}
where 
\begin{align*}
  &\dom(\hs_{f1}) = [\mathtt{f1}-2,\mathtt{1f}] \\
  &\dom(\hs_\flag) = [\flag,\flag] \\
  &\dom(\ms_\link) = [\link,\link+1]\\
  &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
  &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc}]} \text{ for all } n
\end{align*}
and
\begin{itemize}
\item The first address of $\hs_{f1}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f1}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f1}$ contains the code of $f1$.
\item $\ms_\flag = [flag \mapsto 0]$
\item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
\item $\hs_\adv$ contains a global read-only capability for $\hs_\link$ on its first address. The remaining cells of the memory segment only contain instructions.
\end{itemize}
if 
  \[
    (\reg_0\update{\pcreg}{c_{f1}},m) \step[n] (\halted,m'),
  \]
then
\[
  m'(\flag) = 0
\]  
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:correctness-f1}]

@@

\begin{lemma}
  For all $n \in \nats$
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+2) \\
    c_{f2} & \defeq ((\rwx,\glob),\mathtt{f2}-2,\mathtt{2f},\mathtt{f2}) \\
    c_{\var{stk}} & \defeq ((\rwlx,\local),\start_\stk,\addrend_{\adv},\start_\stk-1) \\
    m & \defeq \hs_{f1} \uplus 
        \hs_\flag \uplus                
        \ms_{\var{link}} \uplus 
        \hs_\adv \uplus 
        m_{\malloc} \uplus 
        \ms_{\var{stk}}
        \ms_{\var{frame}} 
  \end{align*}
  where 
  \begin{align*}
    &\dom(\hs_{f2}) = [\mathtt{f2}-2,\mathtt{2f}] \\
    &\dom(\hs_\flag) = [\flag,\flag] \\
    &\dom(\ms_\link) = [\link,\link+1]\\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc}]} \text{ for all } n
  \end{align*}
  and
  \begin{itemize}
  \item The first address of $\hs_{f2}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f2}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f2}$ contains the code of $f2$.
  \item $\ms_\flag = [flag \mapsto 0]$
  \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
  \item $\ms_\stk(a) = 0$ for all $a \in [\start_\stk, \addrend_\stk]$
  \item $\hs_\adv$ is only instructions and possibly a global read-only capability for $\hs_\link$
  \end{itemize}
  if 
  \[
    (\reg_0\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m'),
  \]
  then
  \[
    m'(\flag) = 0
  \]  
\end{lemma}

>>>>

\begin{specification}[Malloc v.2]
  $c_\malloc$ satisfies the specification for malloc iff
\[  
  \left\{
  \begin{aligned}
    &\forall \Phi \in \ExecConfs \ldotp \forall m_{\var{footprint}} \in \Heaps\ldotp \hsframe \in \HeapSegments \ldotp \\
    &\quad \forall n, \size \in \nats \ldotp \forall b,e,a \in \Addrs\ldotp\forall p \in \Perms \ldotp \forall W \in \Worlds \ldotp\\
    &\qquad \exists i, \iota_{\malloc,0} \ldotp \\
    &\qquad \quad \forall \iota_\malloc \futurewk \iota_{\malloc,0} \land \\
    &\qquad \quad \memheap = m_{\var{footprint}} \uplus \hsframe \land\\
    &\qquad \quad \heapSat[m_{\var{footprint}}]{n}{[i \mapsto \iota_\malloc]} \land \\
    &\qquad \quad \memreg(r_1) = \size \land \\
    &\qquad \quad \size \geq 0 \land \\
    &\qquad \quad \memreg(r_0) = (p,b,e,a) \land \\
    &\qquad \quad \memreg(\pcreg) = c_\malloc \\ %and this needs to change with ABI.
    &\qquad \quad \Rightarrow \\
    &\qquad \qquad\exists \Phi' \in \ExecConfs \ldotp \exists m_{\var{footprint}}' \in \Heaps\ldotp \exists \ms_{\var{alloc}} \in \HeapSegments\ldotp\\
    &\qquad \qquad \quad \exists j,k \in \nats \ldotp \exists b',e'\in \Addrs \ldotp \exists W' \in \Worlds \ldotp \\
    &\qquad \qquad \qquad \Phi \step[j]\Phi' \land \\
    &\qquad \qquad \qquad \memheap[\Phi']=m_{\var{footprint}}' \uplus \hs_{\var{alloc}} \uplus \hsframe \land\\
    &\qquad \qquad \qquad  \iota_{\malloc}' \futurewk \iota_{\malloc}\\
    &\qquad \qquad \qquad \heapSat[m_{\var{footprint}}']{n-j}{[i \mapsto \iota_{\malloc}']} \land \\
    &\qquad \qquad \qquad \dom(\hs_{\var{alloc}}) = [b',e'] \land \forall a \in [b',e']\ldotp \hs_{\var{alloc}}(a) = 0  \land \\
    &\qquad \qquad \qquad \memreg[\Phi'] = \memreg[\Phi]\update{\pcreg}{\updatePcPerm{(p,b,e,a)}}\update{r_1}{((\rwx,\glob),b',e',b')} \land \\
    &\qquad \qquad \qquad \size = e'-b' \land\\
  \end{aligned}\right.
\]
where $\iota_{\malloc,0}$ is the region that initially governs malloc 
\end{specification}
In the specfication above $\iota_\malloc'$ is a future region of the initial region that governs malloc.

@@

\begin{lemma}[Correctness lemma for \texttt{f1}] \forcenewline
\label{lem:correctness-f1}
  For all $n \in \nats$
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+2) \\
    c_{f1} & \defeq ((\rwx,\glob),\mathtt{f1}-2,\mathtt{1f},\mathtt{f1}) \\
    c_\malloc & \defeq ((\entry,\glob),\start_\malloc,\addrend_\malloc,\start_\malloc+2) \\
    m & \defeq \hs_{f1} \uplus 
               \hs_\flag \uplus                
               \ms_{\var{link}} \uplus 
               \hs_\adv \uplus 
               m_{\malloc} \uplus 
               \hs_{\var{frame}} 
  \end{align*}
where 
\begin{align*}
  &\dom(\hs_{f1}) = [\mathtt{f1}-2,\mathtt{1f}] \\
  &\dom(\hs_\flag) = [\flag,\flag] \\
  &\dom(\ms_\link) = [\link,\link+1]\\
  &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
  &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]} \text{ for all } n
\end{align*}
and
\begin{itemize}
\item The first address of $\hs_{f1}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f1}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f1}$ contains the code of $f1$.
\item $\ms_\flag = [flag \mapsto 0]$
\item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
\item $\hs_\adv$ contains a global read-only capability for $\hs_\link$ on its first address. The remaining cells of the memory segment only contain instructions.
\end{itemize}
if 
  \[
    (\reg_0\update{\pcreg}{c_{f1}},m) \step[n] (\halted,m'),
  \]
then
\[
  m'(\flag) = 0
\]  
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:correctness-f1}]
Let $n$ be given and assume the premisses in the lemma.  Consider the following part of the execution:
  \[
    (\reg_0\update{\pcreg}{c_{f1}},m) \step[i] (\reg_0\update{\pcreg}{c_\malloc}\update{r_0}{c_{f1}'}\update{r_1}{1},m)
  \]
Where $c_{f1}'$ is the return address. Use the malloc specification with
\begin{align*}
  W &= [0 \mapsto \iota_{\malloc,0}] \\
  m_{\var{footprint}} & = m_\malloc \\
  size & = 1
\end{align*}
to get 
\[
(\reg_0\update{\pcreg}{c_\malloc}\update{r_0}{c_{f1}'}\update{r_1}{1},m) \step[j] (\reg_0\update{\pcreg}{c_{f1}'}\update{r_0}{c_{f1}'}\update{r_1}{c_l},m')
\]
where for some $W' \futurewk W$
\begin{align*}
  m' & = \hs_{f1} \uplus 
         \hs_\flag \uplus                
         \ms_{\var{link}} \uplus 
         \hs_\adv \uplus 
         \ms_{\var{alloc}} \uplus
         m_{\malloc}' \uplus 
         \hs_{\var{frame}} 
\end{align*}

@@

\begin{lemma}
  For all $n \in \nats$
  let
  \begin{align*}
    c_{\var{adv}} & \defeq ((\entry,\glob),\start_{\adv},\addrend_{\adv},\start_{\adv}+2) \\
    c_{f2} & \defeq ((\rwx,\glob),\mathtt{f2}-2,\mathtt{2f},\mathtt{f2}) \\
    c_{\var{stk}} & \defeq ((\rwlx,\local),\start_\stk,\addrend_{\adv},\start_\stk-1) \\
    m & \defeq \hs_{f1} \uplus 
        \hs_\flag \uplus                
        \ms_{\var{link}} \uplus 
        \hs_\adv \uplus 
        m_{\malloc} \uplus 
        \ms_{\var{stk}}
        \ms_{\var{frame}} 
  \end{align*}
  where 
  \begin{align*}
    &\dom(\hs_{f2}) = [\mathtt{f2}-2,\mathtt{2f}] \\
    &\dom(\hs_\flag) = [\flag,\flag] \\
    &\dom(\ms_\link) = [\link,\link+1]\\
    &\dom(\ms_\stk) = [\start_\stk, \addrend_\stk]\\
    &\dom(\hs_{\adv}) = [\start_\adv,\addrend_\adv] \\
    &\heapSat[\hs_{\malloc}]{n}{[0 \mapsto \iota_{\malloc,0}]} \text{ for all } n
  \end{align*}
  and
  \begin{itemize}
  \item The first address of $\hs_{f2}$ contains a global read-only capability for $\hs_\link$, the second address of $\hs_{f2}$ contains a global read-write capability to $\hs_\flag$, the rest of $\hs_{f2}$ contains the code of $f2$.
  \item $\ms_\flag = [flag \mapsto 0]$
  \item $\ms_{\var{link}} = [\var{link} \mapsto c_\malloc, \var{link} + 1 \mapsto c_\adv]$
  \item $\ms_\stk(a) = 0$ for all $a \in [\start_\stk, \addrend_\stk]$
  \item $\hs_\adv$ is only instructions and possibly a global read-only capability for $\hs_\link$
  \end{itemize}
  if 
  \[
    (\reg_0\update{\pcreg}{c_{f2}}\update{r_\stk}{c_\stk},m) \step[n] (\halted,m'),
  \]
  then
  \[
    m'(\flag) = 0
  \]  
\end{lemma}
